Waveform and Passive Beamforming Design for Intelligent Reflecting Surface-Aided Wireless Information and Power Transfer

### 2020-09-04 main.tex
:pencil: Path loss and noise power

\begin{section}{Performance Evaluations}
	To evaluate the performance of the proposed IRS-aided SWIPT system, we characterize and compare typical R-E regions under different setups. Consider a large open space WiFi-like environment at a center frequency of 5.18 \si{GHz} with bandwidth $B=1$ \si{MHz}. As shown in Figure \ref{fi:layout}, we assume the IRS moves along a horizontal line that is parallel to the AP-user path. Define the projection of the AP-IRS path onto the AP-user path as $d_H$ and let the distance from the IRS to the AP-user path be $d_V$. Denote $d_D$, $d_I$, $d_R$ as the length of direct, incident, reflective paths. We set $d_D=15$ \si{\meter}, $d_V=2$ \si{\meter} and choose a reference $d_H=2$ \si{\meter}. For all channels, the path loss and power delay profile of the frequency-selective fading are obtained from IEEE TGn channel model D \cite{Erceg2004}. Reference path loss is set to $L_0=-35$ \si{\dB} at $d_0=1$ \si{\meter} such that the equivalent path loss of AP-user and AP-IRS-user links is $L=-58.61$ \si{\dB}. Taps are modelled as i.i.d. CSCG random variables with normalized total power, and we assume no spatial correlation across all arrays. Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\text{ant}}=50$ \si{\ohm}. The average Effective Isotropic Radiated Power (EIRP) is fixed to $-36$ \si{\dBi} while the reference average noise power is $\sigma_n=-60$ \si{\dBm} at all subbands, corresponding to a large-scale SNR of $19.39$ \si{\dB}. We also assume 0 \si{\dBi} IRS element gain and 2 \si{\dBi} receive antenna gain. For the algorithm, the tolerance is $\epsilon=10^{-8}$ and the number of candidates in the Gaussian randomization method is $Q=10^{3}$.

>>>>

\begin{section}{Performance Evaluations}
	To evaluate the performance of the proposed IRS-aided SWIPT system, we characterize and compare typical R-E regions under different setups. Consider a large open space WiFi-like environment at a center frequency of 5.18 \si{GHz} with bandwidth $B=1$ \si{MHz}. As shown in Figure \ref{fi:layout}, we assume the IRS moves along a horizontal line that is parallel to the AP-user path. Define the projection of the AP-IRS path onto the AP-user path as $d_H$ and let the distance from the IRS to the AP-user path be $d_V$. Denote $d_D$, $d_I$, $d_R$ as the length of direct, incident, reflective paths. We fix $d_D=15$ \si{\meter}, $d_V=2$ \si{\meter} and choose a reference $d_H=2$ \si{\meter}. For all channels, the path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}. Reference path loss is set to $L_0=-35$ \si{\dB} at $d_0=1$ \si{\meter} such that the reference path loss of direct, incident and reflective links are $L_D=-61.16$ \si{\dB}, $L_I=-44.03$ \si{\dB} and $L_R=-59.17$ \si{\dB}, respectively. Taps are modelled as i.i.d. CSCG random variables with normalized total power, and we assume no spatial correlation across all arrays. Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\text{ant}}=50$ \si{\ohm}. The average Effective Isotropic Radiated Power (EIRP) is fixed to $-36$ \si{\dBi} while the reference average noise power is $\sigma_n=-60$ \si{\dBm} at all subbands. We also assume 0 \si{\dBi} IRS element gain and 2 \si{\dBi} receive antenna gain. For the algorithm, the tolerance is $\epsilon=10^{-8}$ and the number of candidates in the Gaussian randomization method is $Q=10^{3}$.
